Too many colors spoil the graph

### 2024-06-20 text/23/modified-power-prior.Rmd
Update 2023 files, part 2

---
title: "The modified power prior"
source: "New"
date: "2023-03-04"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

>>>>

---
title: "The modified power prior"
source: "New"
date: "2023-03-04"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---

### 2024-06-20 text/23/normal-hedging-hyperprior-part-2.Rmd
Update 2023 files, part 2

---
title: "The hedging hyperprior for the normal distribution: known mean, unknown precision"
source: "New"
date: "2023-03-14"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

>>>>

---
title: "The hedging hyperprior for the normal distribution: known mean, unknown precision"
source: "New"
date: "2023-03-14"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---

### 2024-06-20 text/23/normal-hedging-hyperprior-part-3.Rmd
More formula updates on hedging hyperprior
Update 2023 files, part 2

---
title: "The hedging hyperprior for the normal distribution: unknown mean, unknown precision"
source: "New"
date: "2023-03-21"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

@@

>>>>

---
title: "The hedging hyperprior for the normal distribution: unknown mean, unknown precision"
source: "New"
date: "2023-03-21"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---

@@

### A simple numerical example

### 2024-06-20 text/23/too-many-colors.rmd
Update 2023 files, part 2

---
title: Too many colors spoil the graph
source: "New"
author: Steve Simon
date: 2023-09-12
categories:
- Blog post
tags:
- Being updated
output: word_document
---

>>>>

---
title: Too many colors spoil the graph
source: "New"
author: Steve Simon
date: 2023-09-12
categories:
- Blog post
tags:
- Being updated
output: word_document
page_update: complete
---
